Simulating a flock of birds

### 2017-10-28 tex/article.tex
comment on figure

>>>>

\todo{
TO EDIT
For the disordered phase $v_a$ is aproximatively 0, while for the ordered phase $v_a$ has the value of 1.
%rephrase:
In the following figure we show how $v_a$ varies with the noise $\eta$ and density  $\rho$ for a constant value of density and noise respectively.

As it can be seen from the graph the overall alignment of the particles depends on the noise and for a high number of particles N the system becomes more disordered.

For high values of density the flock reaches a coherent moving phase, while for low values of density the particles move randomly in the lattice.

TO EDIT

}
